ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE:

### 2015-07-02 paper/wish/wsc15paper.tex
changes

\citeN{Frazier:BIZ} presents a new sequential elimination
IZ procedure, called BIZ (Bayes-inspired Indifference Zone), 
that eliminates the use of Bonferroni's inequality, reducing conservatism. \mathcal
This procedure's lower bound on the worst-case probability of correct selection in the
preference zone is tight in continuous time, and almost tight in discrete time. In numerical experiments, the number of samples required
by BIZ is significantly smaller than that of procedures like the ${P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968} and the KN procedure of \citeN{Kim:2001}, especially on problems with many alternatives. Unfortunately, the
proof from \citeN{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
(2) variances are known;
and (3) the variances are either common across alternatives, or have an unrealistic integer multiple structure.

>>>>

\citeN{Frazier:BIZ} presents a new sequential elimination
IZ procedure, called BIZ (Bayes-inspired Indifference Zone), 
that eliminates the use of Bonferroni's inequality, reducing conservatism. 
This procedure's lower bound on the worst-case probability of correct selection in the
preference zone is tight in continuous time, and almost tight in discrete time. In numerical experiments, the number of samples required
by BIZ is significantly smaller than that of procedures like the ${P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968} and the KN procedure of \citeN{Kim:2001}, especially on problems with many alternatives. Unfortunately, the
proof from \citeN{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
(2) variances are known;
and (3) the variances are either common across alternatives, or have an unrealistic integer multiple structure.
